Figures

### 2022-12-14 manuscript/figures.Rmd
more specific description of dashed line

```{r fig.cap="Censored lake area edf (solid line) and transformed cdf estimate (dashed line) compared against the HydroLAKES dataset.", echo=FALSE, fig.width=1,out.height="4in"}
knitr::include_graphics("../manuscript/figures/predict_censor-1.pdf")
```

```{r fig.cap="Stan model code", echo=FALSE, fig.width=1,out.height="5in"}
knitr::include_graphics("../manuscript/figures/stan.pdf")
```

>>>>

```{r fig.cap="Simulated lake area (blue line) where the portion (>= 0.1 $km^2$) calculated from the edf is denoted by a solid line and the portion (< 0.1 $km^2$) calculated from the transformed cdf is denoted by a dashed line. For comparison, the edf of the HydroLAKES dataset (red line) is also shown.", echo=FALSE, fig.width=1,out.height="4in"}
knitr::include_graphics("../manuscript/figures/predict_censor-1.pdf")
```
